A geographic routing approach for IPv6 in low-powered and lossy large-scale wireless networks

### 2015-03-27 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
correção no algoritmo no passo 3
atualização do asbtract

\begin{abstract}
%% Text of abstract
In this paper, we propose \sout{a routing protocol for a smart street lighting system based on IPv6-enabled wireless sensor network} \rev{\textit{GeoRank}, a geographic routing approach for the IPv6-enabled large-scale  wireless networks}. We discuss the main drawbacks of the RPL (IPv6 Routing Protocol for
Low-Power and Lossy Networks) for P2P (point-to-point) communication in large-scale 6LoWPAN networks. Then, we address such drawbacks by proposing a new routing \sout{algorithm} \rev{protocol}, named \textit{GeoRank}, which integrates RPL protocol with the position-based routing protocol GOAFR (Greedy Other Adaptive Face Routing). Simulations were performed on networks extracted from real street maps. The obtained results show that \textit{GeoRank} finds shorter routes than RPL in high link density conditions and than GOAFR in low link density conditions. Thus, \textit{GeoRank} shows to be adaptive to variable link densities found in large-scale networks. Further, \textit{GeoRank} avoids the use of DAO (Destination Advertisement Object) control messages required in RPL, while being more scalable in terms of memory usage than storing-mode RPL.
\end{abstract}

@@

%Highlights
%
%We propose a smart street lighting system based on a IPv6-enabled wireless sensor networks.
%Main drawbacks of RPL protocol for P2P communication are discussed.
%We propose a new routing algorithm, termed GeoRank, which integrates RPL protocol with GOAFR geographic routing protocol.
%Simulations were performed on networks extracted from real street maps.
%Results show that GeoRank performs better in large-scale networks with variable link densities than GOAFR or RPL protocols alone.
%We discuss the scalability of GeoRank in terms of memory and bandwidth consumption in comparison to RPL protocol.

%- We propose a smart street lighting system based on IPv6-enabled wireless sensor network.
%- Main drawbacks of RPL protocol for P2P communication are discussed.
%- We propose a new routing algorithm, GeoRank, which integrates RPL and GOAFR protocols.
%- Simulations were performed on networks extracted from real street maps.
%- GeoRank is adaptive to variable link densities found in large-scale networks.
%- We discuss the scalability of GeoRank in comparison to RPL protocol.

%- We propose a smart street lighting system based on IPv6-enabled wireless sensor network.
%- Main drawbacks of RPL protocol for P2P communication are discussed.
%- GeoRank, a new routing algorithm is proposed and its scalability is compared to RPL.
%- Simulations were performed on networks extracted from real street maps.
%- GeoRank is adaptive to variable link densities found in large-scale networks.

@@

\STATE \textbf{3. GeoRank mode:} If the destination node is closer to the anchor node $j$ (stored in the packet being routed) than the current node holding the packet $u$, forward the packet to the DODAG Preferred Parent $v \in DDP(u,j)$. Repeat such process until : \textbf{a)} the packet reaches a node $u$ whose position is closer to the destination than the position stored in the packet at step 2; \textbf{b)} the packet reach the DODAG root $j$; \textbf{c)} the packet reach the destination node. If condition ``a'' is met, go back to step 2. If condition ``b'' or ``c'' is satisfied, go to step 4.

>>>>

\begin{abstract}
%% Text of abstract
In this paper, we propose \sout{a routing protocol for a smart street lighting system based on IPv6-enabled wireless sensor network} \rev{\textit{GeoRank}, a geographic routing approach for the IPv6-enabled large-scale  wireless networks}. We discuss the main drawbacks of the RPL (IPv6 Routing Protocol for
Low-Power and Lossy Networks) for P2P (point-to-point) communication in large-scale 6LoWPAN networks. Then, we address such drawbacks by proposing a \sout{new} routing \sout{algorithm} \rev{protocol}, named \textit{GeoRank}, which integrates RPL protocol with the position-based routing protocol GOAFR (Greedy Other Adaptive Face Routing). \sout{Simulations were performed on networks extracted from real street maps.} The \sout{obtained} results \rev{obtained with simulations} show that \textit{GeoRank} finds shorter routes than RPL in high link density conditions and than GOAFR in low link density conditions. Thus, \textit{GeoRank} shows to be adaptive to variable link densities found in large-scale networks. Further, \textit{GeoRank} avoids the use of DAO (Destination Advertisement Object) control messages required in RPL, while being more scalable in terms of memory usage than storing-mode RPL.
\end{abstract}

@@

%Highlights
%
%?	We combine RPL and GOAFR protocols for IPv6-enabled large-scale wireless networks.
%?	Main drawbacks of the RPL protocol for P2P communication are discussed.
%?	A routing protocol (GeoRank) is proposed and its scalability is compared to RPL.
%?	Simulations were performed on networks extracted from real street maps.
%?	GeoRank is adaptive to variable link densities found in large-scale networks.

@@

\STATE \textbf{3. GeoRank mode:} If the destination node is closer to the anchor node $j$ (stored in the packet being routed) than the current node holding the packet $u$, forward the packet to the DODAG Preferred Parent $v \in DDP(u,j)$. Repeat such process until : \textbf{a)} the packet reaches a node $u$ whose position is closer to the destination than the position stored in the packet at step 2; \textbf{b)} the packet reach the DODAG root $j$; \textbf{c)} the packet reach the destination node. If condition ``a'' is met, go back to step 2. If condition ``b'' is satisfied, go to step 4.
